### 2015-03-18 bugfinding.tex
update to table

By default, \corral instruments a \texttt{yield} statement (which denotes a preemption) before every \emph{visible operation} (i.e. synchronisation operations and shared memory accesses) of a concurrently running thread. It then sequentialises the concurrent program with a schedule that explores all possible interleavings up to a pre-defined bound.

Our idea for accelerating \corral is simple: we simplify the sequentialisation that \corral performs by removing \texttt{yield} statements from all shared memory accesses that \whoop has soundly proved to not be racy. We basically perform a partial order reduction that can significantly reduce the interleavings that \corral needs to explore, and thus increase performance and scalability.

@@

>>>>

By default, \corral instruments a \texttt{yield} statement (which denotes a context-switch) before each \emph{visible operation} (i.e. synchronisation operations and shared memory accesses) of a concurrently running thread. It then sequentialises the concurrent program with a schedule that explores all possible interleavings up to a pre-defined bound.

Our idea for accelerating \corral is simple: we simplify the sequentialisation that \corral performs by instrumenting \texttt{yield} statements only in shared memory accesses that \whoop reported as potentially racy. This effectively acts as a partial order reduction that can significantly reduce the interleavings that \corral needs to explore, and thus increase performance and scalability.

@@

\subsection{Granularity of Context-Switches}
\label{bf:granularity}

As aforementioned, \corral instruments by default a \texttt{yield} statement in each visible operation. Using information from \whoop, though, we can avoid instrumenting context-switches in memory accesses that do not race. To achieve this, we use the \corral command line option \texttt{/cooperative}, which disables \texttt{yield} instrumentation in \corral, and then we instrument context-switches inside \whoop before sending these Boogie files to \corral. We have implemented two different levels of context-switch instrumentation granularity: \emph{\yieldcoarse} and \emph{\yieldmr}.

\yieldcoarse instruments \texttt{yield} statement in a binary fashion: if \whoop finds that a pair of entry points cannot race, then it will only instrument context-switches in synchronisation points of this pair; else if \whoop finds that a pair of entry points can race, then it will instrument context-switches in all visible operations of this pair.

\yieldmr is a finer-grained instrumentation: \whoop instruments context-switches in all synchronisation points, but only instruments context-switches in memory regions that can potentially race (regardless if a pair has not been fully verified as race-free). In our experiments (see Section~\ref{evaluation}), \yieldmr performs significantly faster than \yieldcoarse.

### 2015-03-18 evaluation.tex
update to table

@@

We evaluate our methodology against 10 modules taken from the Linux kernel (currently a mix of latest and older distributions).

\subsection{Granularity of Yield Instrumentation}
\label{eval:granularity}

@@

Granularities: Yield-All (\corral without \whoop); \yieldcoarse; \yieldmr

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rr rr r r}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Results ...}
\label{tab:granularity}
\end{table*}

The machzwd watchdog driver explodes when running on vanilla \corral, because in some entry point pairs it attempts to analyse a large number of memory regions. For example for the entry point pair write vs init, it instruments interleavings at 26 different memory regions in a single invocation of \corral, which required approximately 1000 seconds to analyse. The same entry point pair is found race-free by \whoop. Using this information in \corral with the \yieldmr instrumentation, the pair takes less than a second to analyse. The \yieldcoarse instrumentation does not perform as well, because it works in the binary granularity of racy or non-racy entry points.

Our experiments used the default \corral context switch bound \texttt{/k:2}. A higher context switch bound would result into deeper interleavings being explored and thus a larger sequentialised program. Intuitively, this means that we would see even greater speedups using information from \whoop, when exploring deeper interleavings. \PDComment{We should take a few measurements with higher k -- no need to be in the table -- just to verify this argument.}

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rr rr r r}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Results ...}
\label{tab:races}
\end{table*}

@@

We evaluate our methodology against 10 modules taken from the Linux kernel (currently a mix of latest and older distributions). \PDComment{Say something about the benchmarks}

\subsection{Context-Switch Granularity of Yield Instrumentation}
\label{eval:granularity}

@@

Our experiments use the default \corral context switch bound \texttt{/k:2}. A higher context switch bound would result into deeper interleavings being explored and thus a larger sequentialised program. Intuitively, this means that we would see even greater speedups using information from \whoop, when exploring deeper interleavings. \PDComment{We should take a few measurements with higher k -- no need to be in the table -- just to verify this argument.}

When running \corral on its own, it can potentially report a spurious race (that \whoop does not report), because \corral is not enhanced with domain-specific information that \whoop uses to discard spurious races. Using \whoop + \corral, though, will inherently discard spurious data races (assuming a precise environmental model).

In Table~\ref{tab:races}, we can notice that \whoop is much faster than \corral. For exampl, \whoop analyses the dtlk char driver in 6.51 seconds, whereas \corral requires 1287.05 seconds.

When \corral on its own tries to analyse the machzwd watchdog driver it explodes, because in some entry point pairs it attempts to analyse a large number of memory regions. For example for the entry point pair write vs init, it instruments interleavings at 26 different memory regions in a single invocation of \corral, which required approximately 1000 seconds to analyse. The same entry point pair is found race-free by \whoop. Using this information in \corral with the \yieldmr instrumentation, the pair takes less than a second to analyse. The \yieldcoarse instrumentation does not perform as well, because it works in the binary granularity of racy or non-racy entry points.
